---
title: "RMarkdown Test 3"
author: "Rick"
date: "12/01/2021"
output: 
  html_document:
    code_folding: "show"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
```


```{r load, Libraries}
library(tidyverse)
library(knitr)

mtcars <- mtcars
```

In this tutorial we will provide: blah blah blah!
For shortcuts see below:

- **bold text** and _bold text_
- *italics text* and _italics text_
- superscript^2^
- Subscript~0~
- ~~strikethrough~~
- embedded links such as [link](www.rstudio.com)

You can create white space with this character

<br>

and you can create a faint horizontal rule this way:

***

You can create a range of headers like below:

# Biggest header
## Second biggest header
###Third biggest header
#### Fourth buggest header
##### Fifth biggest header
###### Smallest header

We can embed equations by putting a dollar sign before and after: $E = M * C^{2}$

RCode can also be embedded in the following way. Suppose I want to return the mean of the 'hp' variable from the 'mtcars' dataset, when code is surrounded by back ticks and the letter r this can be done. For example, the mean is `r mean(mtcars$hp)`. As mentioned earlier, a new code chunk can be created by enclosing code by a pair of ```

A list can be created like this:

* unordered list
* item 2
  + sub-item 1
  + sub-item 2
  
1. ordered list
2. item 2
  + sub-item 1
  + sub-item 2
  
A table can be created like this:

First header | Second header
-------------|--------------
Content cell | Content cell
Content cell | Content cell
Content cell | Content cell

However, creating tables can be more interesting that this.

Conside the following:

```{r}
head(mtcars)
```

```{r}
kable(head(mtcars))
```

